\documentclass[11pt,letterpaper]{article}
\usepackage{style}

\begin{document}
\datefooter

\header{}

\section*{Summary}
LLM engineer and researcher at Huawei Canada specializing in coding agents and agent evaluation. ACL 2026 and ICML 2026 publications on interpretable dialogue and multi-agent LLM safety; contributor to Harbor (Terminal-Bench's official harness) and NVIDIA's NeMo Guardrails. Build LLM-driven systems that are capable, controllable, and reliable.

\section*{Experience}

\entry{Associate LLM Engineer}{\href{https://www.huawei.com/}{Huawei Canada}}{Kingston, ON, Canada}{Sep.\ 2025 -- Present}
\begin{itemize}
  \item Improved a coding-agent scaffold, boosting performance by \textbf{>15\%} on SWE-Bench Verified.
  \item Analyzed agent outputs on LiveCodeBench; surfaced model-side anomalies and harness/eval defects.
  \item Lifted gold-patch resolution on FeatBench from \textbf{37.31\%}\,{\footnotesize$\pm$\,1.88} to \textbf{99.81\%}\,{\footnotesize$\pm$\,0.10} by diagnosing harness and environment defects in the original benchmark; released FeatBench-Verified v1.3 to the community.
\end{itemize}

\entry{Big Data Engineer}{\href{https://bale.ai/}{Bale Messenger}}{Tehran, Iran}{Mar.\ 2023 -- Aug.\ 2023}
\begin{itemize}
  \item Developed and maintained robust big data pipelines for continuous data ingestion and processing on the Bale financial-messaging platform, enhancing data reliability and real-time accessibility.
  \item Implemented scalable solutions with Apache Spark, Hive, and Kafka, significantly improving data-warehousing efficiency and scalability.
\end{itemize}

\entry{Machine Learning Engineer \& Backend Developer}{Sharif Data Analytics Lab \& National Elites Foundation of Iran}{Tehran, Iran}{Dec.\ 2021 -- Sep.\ 2022}
\begin{itemize}
  \item Trained a speaker-verification system (part of an Intelligent Voice Commands product) leveraging the state-of-the-art \href{https://arxiv.org/abs/2104.01466}{ECAPA-TDNN} model, achieving over 97\% accuracy on a custom 8,400-pair dataset.
\end{itemize}

\section*{Education}

\entry{M.A.Sc., Electrical and Computer Engineering}{Queen's University, Kingston, ON, Canada}{GPA: A+}{Sep.\ 2023 -- Sep.\ 2025}
\begin{itemize}
  \item Thesis: \textit{CoDial: Interpretable Task-Oriented Dialogue Systems Through Dialogue Flow Alignment} (Prof.\ X.\ Zhu). Published at ACL 2026.
\end{itemize}

\entry{B.Sc., Computer Engineering}{Amirkabir University of Technology, Tehran, Iran}{GPA: 19.45 / 20 --- Ranked 1st of 156}{Sep.\ 2018 -- Apr.\ 2023}
\begin{itemize}
  \item B.Sc.\ Project: \textit{Generating Handwritten Persian Characters with Generative Models} (Prof.\ A.\ Nickabadi).
\end{itemize}

\section*{Publications}

\pubentry
  {\href{https://arxiv.org/abs/2506.02264}{CoDial: Interpretable Task-Oriented Dialogue Systems Through Dialogue Flow Alignment}}
  {\textbf{Radin Shayanfar}, Chu Fei Luo, Rohan V.\ Bhambhoria, Samuel Dahan, Xiaodan Zhu.}
  {ACL 2026}

\pubentry
  {\href{https://arxiv.org/abs/2506.11083}{RedDebate: Safer Responses through Multi-Agent Red Teaming Debates}}
  {Ali Asad, Stephen Obadinma, \textbf{Radin Shayanfar}, Xiaodan Zhu.}
  {ICML 2026}

\pubentry
  {\href{https://centre-for-software-excellence.github.io/docs/blog/before-you-score-the-model-score-the-benchmark}{Before You Score the Model, Score the Benchmark: A Skeptical View Into Current Agentic Software Engineering Benchmarks}}
  {\textbf{Radin Shayanfar}, Keheliya Gallaba.}
  {Blog Post\\May 2026}

\pubentry
  {\href{https://aclanthology.org/2024.findings-emnlp.924/}{Misinformation with Legal Consequences (MisLC): A New Task Towards Harnessing Societal Harm of Misinformation}}
  {Chu Fei Luo, \textbf{Radin Shayanfar}, Rohan V.\ Bhambhoria, Samuel Dahan, Xiaodan Zhu.}
  {EMNLP 2024\\(Findings)}

\section*{Open-Source Contributions}

\entry{\href{https://github.com/harbor-framework/harbor}{Harbor Framework}}{Agent-evaluation harness and RL-environment framework from the creators of Terminal-Bench}{Contributor}{2026}
\begin{itemize}
  \item Authored the \textbf{FeatBench} Harbor adapter (\href{https://github.com/harbor-framework/harbor/pull/1218}{PR \#1218}) for a 156-task, 25-repo feature-level code-generation benchmark; ported parity fixes upstream to FeatBench and released FeatBench-Verified v1.3, preserving 99\%+ of original instances and tests.
  \item Integrated ByteDance's \textbf{trae-agent} into Harbor (\href{https://github.com/harbor-framework/harbor/pull/1298}{PR \#1298}): full agent implementation, configuration handling, API-key sanitization, and unit tests.
  \item Fixed a deveval oracle env-var bug (\href{https://github.com/harbor-framework/harbor/pull/1431}{PR \#1431}); reviewed the SWE-Gym pytest-xdist fix (\href{https://github.com/harbor-framework/harbor/pull/1438}{PR \#1438}).
\end{itemize}

\entry{\href{https://github.com/NVIDIA-NeMo/Guardrails}{NVIDIA NeMo Guardrails}}{Toolkit for programmable guardrails on LLM-based conversational systems}{Contributor}{2024}
\begin{itemize}
  \item Fixed the Colang~2 parser to correctly handle nested \texttt{if/else} statements (\href{https://github.com/NVIDIA-NeMo/Guardrails/pull/833}{PR \#833}).
  \item Resolved multiline output rendering in few-shot prompts (\href{https://github.com/NVIDIA-NeMo/Guardrails/pull/765}{PR \#765}) and dynamic flow generation (\href{https://github.com/NVIDIA-NeMo/Guardrails/pull/748}{PR \#748}).
  \item Added Colang commenting support (\texttt{Ctrl+/}) to the VSCode extension (\href{https://github.com/NVIDIA-NeMo/Guardrails/pull/749}{PR \#749}).
\end{itemize}

\section*{Selected Projects}

\entry{\href{https://github.com/radinshayanfar/transformer}{Transformer from Scratch}}{PyTorch, Transformer, Machine Translation, BPE Tokenization}{}{Summer 2025}
\begin{itemize}
  \item Implemented the original Transformer in PyTorch (encoder-decoder, encoder-only, decoder-only) solely from the paper.
  \item Built a complete WMT translation system: data loading, BPE tokenization, masking, training loop, and evaluation.
\end{itemize}

\entry{\href{https://github.com/radinshayanfar/speechbrain}{Speaker-Specific Voice Activity Detection}}{PyTorch, SpeechBrain, VAD, Speaker Verification}{}{Fall 2024}
\begin{itemize}
  \item Proposed a Speaker-Specific VAD framework integrating ECAPA-TDNN embeddings into a CRDNN-based VAD; extended SpeechBrain to support conditioning on target-speaker embeddings.
  \item Achieved low Diarization Error Rate on the AMI dataset under real-time, multi-speaker conditions.
\end{itemize}

\section*{Skills}
\begin{itemize}
  \item \textbf{Programming:} Python, Go, Java, C, JavaScript.
  \item \textbf{LLMs \& Agents:} LLM Coding Agents, Agent Evaluation \& Benchmarking, Harbor Framework, LangChain, NeMo Guardrails, RAG, Pinecone.
  \item \textbf{ML \& NLP:} PyTorch, HuggingFace Transformers, SpeechBrain, Keras.
  \item \textbf{Infra \& Tools:} Docker, Kubernetes, Linux, Git, Apache Spark, Kafka.
  \item \textbf{Languages:} Persian (native); English (proficient; TOEFL 109/120).
\end{itemize}

\end{document}
