%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------    
  \cventry
    {Big Data Engineer} % Job title
    {\href{https://bale.ai/}{Bale Messenger}} % Organization
    {Tehran, Iran} % Location
    {Mar. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained robust \textbf{big data pipelines} for continuous data ingestion and processing in Bale (Financial) Messenger platform, enhancing data reliability and real-time accessibility.}
        \item {Implemented scalable solutions utilizing \textbf{Apache Spark}, \textbf{Hive}, and \textbf{Kafka}, significantly improving the efficiency and scalability of the data warehousing.}
      \end{cvitems}
    }

%---------------------------------------------------------    
%  \cventry
%    {Reasearch Assistant} % Job title
%    {\href{https://www.ualberta.ca/index.html}{University of Alberta}} % Organization
%    {} % Location
%    {Oct. 2022 - PRESENT} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Working on \textbf{trustworthy machine learning} for software engineering.}
%        \item {Under supervision of Dr. A. Esmaeilzehi, postdoctoral research fellow at Momentum Lab, University of Alberta.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer, Backend Developer} % Job title
    {\href{https://www.sharif.edu/}{Sharif Data Analytics Lab} \& \href{https://en.bmn.ir/}{National Elites Foundation of Iran}} % Organization
    {Tehran, Iran} % Location
    {Dec. 2021 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Worked on an \textbf{Intelligent Voice Commands Recognition} system. Under supervision of Prof.~S.~A.~Motahari.}
        \item{Trained a \textbf{speaker verification system}, part of an Intelligent Voice Commands Recognition system, leveraging state-of-the-art \href{https://arxiv.org/abs/2104.01466}{\textbf{ECAPA-TDNN}} model, achieving over \textbf{97\% accuracy} on a custom dataset consisting of 8,400 sample pairs.}
        \item{Designed and developed a web API using a \textbf{microservices architecture} with \textbf{Flask} and \textbf{Laravel}, streamlining voice command processing and authentication.}
        % \item {My main task was the development of a \textbf{speaker verification} system, in which the authentication is done by user's voice. For this purpose, I trained and evaluated state-of-the-art \href{https://arxiv.org/abs/2104.01466}{ECAPA-TDNN} model on \href{https://commonvoice.mozilla.org}{Common Voice} Persian dataset. The model achieved more than 97\% accuracy on our own collected test set consisting of 8400 pair samples.} % The experiment results are available on \href{https://github.com/radinshayanfar/speaker-verification}{GitHub}.}
        % \item{I was also in charge of the design and development of the system's web API.%, which is utilized in the website (\href{https://rasam-ai.ir/}{rasam-ai.ir}).
        % The API exploits a microservice architecture and is written in PHP and Python with Laravel and Flask frameworks, respectively.}
      \end{cvitems}
    }

%---------------------------------------------------------    
  \cventry
    {Programming Contest Scientific Team Member} % Job title
    {\href{https://samcode.allamehelli3.ir/staff.html}{SamCode 5}} % Organization
    {Tehran, Iran} % Location
    {Sep. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Designed problems and test cases for {\href{https://samcode.allamehelli3.ir/}{SamCode}}, a programming contest for junior high school students.}
        \item{Designed computational problems and comprehensive test cases for \textbf{algorithmic programming contests}, targeting high-achieving junior high school students.}
      \end{cvitems}
    }

%---------------------------------------------------------    
  \cventry
    {Freelancer} % Job title
    {\href{https://ponisha.ir/profile/radinshayanfar}{Ponisha}} % Organization
    {Tehran, Iran} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Developed Telegram applications using Python and Telegram’s TDLib library.}
        \item{Created responsive \textbf{Telegram-based applications} using \textbf{Python} and Telegram’s \textbf{TDLib}, providing robust solutions tailored to diverse client requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------    
\end{cventries}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Teaching Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
    {\href{https://www.queensu.ca/}{Queen's University}} % Job title
    {Teaching Assistant, Machine Learning \& Deep Learning} % Organization
    {} % Location
    {Winter 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~X.~Zhu}
        \item {Supervising labs. Designing and grading exams.}
      \end{cvitems}
    }

\cventry
    {\href{https://www.queensu.ca/}{Queen's University}} % Job title
    {Teaching Assistant, Fundamentals of Information Structure} % Organization
    {} % Location
    {Fall 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~T.~Dean}
        \item {Supervising labs. Grading assignments and exams}
      \end{cvitems}
    }


\cventry
    {\href{https://www.queensu.ca/}{Queen's University}} % Job title
    {Teaching Assistant, Object Oriented Programming} % Organization
    {} % Location
    {Winter 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~M.~Greenspan}
        \item {Grading assignments and quizzes}
      \end{cvitems}
    }

\cventry
    {\href{https://aut.ac.ir/}{Amirkabir University of Technology}} % Job title
    {Teaching Assistant, Multicore Programming} % Organization
    {} % Location
    {Spring 2022 \& 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~M.~Momtazpour}
        \item {Designing theoretical and programming assignments, grading}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://aut.ac.ir/}{Amirkabir University of Technology}} % Job title
    {Teaching Assistant, Computational Intelligence} % Organization
    {} % Location
    {Spring 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~M.~Ebadzadeh}
        \item {Designing programming assignments, giving quizzes, grading}
      \end{cvitems}
    }
    
  \cventry
    {\href{https://aut.ac.ir/}{Amirkabir University of Technology}} % Job title
    {Head Teaching Assistant, Signals and Systems} % Organization
    {} % Location
    {Fall 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~M.~Rasti}
        \item {Designing theoretical and programming assignments, giving quizzes, grading}
      \end{cvitems}
    }
   
%---------------------------------------------------------
  \cventry
    {\href{https://aut.ac.ir/}{Amirkabir University of Technology}} % Job title
    {Teaching Assistant, Data Structures and Algorithms} % Organization
    {} % Location
    {Fall 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~E.~Nazerfard}
        \item {Designing theoretical and programming assignments, grading assignments}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://aut.ac.ir/}{Amirkabir University of Technology}} % Job title
    {Teaching Assistant, Linear Algebra} % Organization
    {} % Location
    {Spring 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Prof.~M.~H.~Chehreghani}
        \item {Designing programming assignments, grading assignments}
      \end{cvitems}
    }

%---------------------------------------------------------        
  \cventry
    {\href{https://aut.ac.ir/}{Amirkabir University of Technology}} % Job title
    {Teaching Assistant, Signals and Systems} % Organization
    {} % Location
    {Spring 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under supervision of Dr.~A.~Aghaeeyan}
        \item {Designing theoretical and programming assignments, grading assignments}
      \end{cvitems}
    }

%---------------------------------------------------------    
\end{cventries}