%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------    
  \cventry
    {Reasearch Assistant} % Job title
    {\href{https://www.ualberta.ca/index.html}{University of Alberta}} % Organization
    {} % Location
    {Oct. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on trustworthy machine learning for software engineering.}
        \item {Under supervision of Dr. A. Esmaeilzehi, postdoctoral research fellow at Momentum Lab, University of Alberta.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer, Backend Developer} % Job title
    {\href{https://www.sharif.edu/}{Sharif Data Analytics Lab} \& \href{https://en.bmn.ir/}{National Elites Foundation of Iran}} % Organization
    {} % Location
    {Dec. 2021 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on an \textbf{Intelligent Voice Commands Recognition} system. Under supervision of \textbf{Prof. S. A. Motahari}.}
        \item {My main task was the development of a \textbf{speaker verification} system, in which the authentication is done by user's voice. I \textbf{trained and evaluated} state-of-the-art \href{https://arxiv.org/abs/2005.07143}{ECAPA-TDNN} model on \href{https://commonvoice.mozilla.org}{Common Voice} Persian dataset. The experiment results are available on \href{https://github.com/radinshayanfar/speaker-verification}{GitHub}.}
        \item{I was also in charge of design and development of the system's \textbf{web API}, which is utilized in the website (\href{https://rasam-ai.ir/}{rasam-ai.ir}). The API exploits a \textbf{microservice} architecture and is written in PHP and Python with Laravel and Flask frameworks respectively.}
      \end{cvitems}
    }

%---------------------------------------------------------    
  \cventry
    {Programming Contest Scientific Team Member} % Job title
    {\href{https://samcode.allamehelli3.ir/staff.html}{SamCode 5}} % Organization
    {} % Location
    {Sep. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed problems and test cases for {\href{https://samcode.allamehelli3.ir/}{SamCode}}, a programming contest for junior high school students.}
      \end{cvitems}
    }

%---------------------------------------------------------    
\end{cventries}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Teaching Experience}

\newcommand{\taprefix}{Teaching Assistant{\enskip\cdotp\enskip}}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {Computational Intelligence} % Course
    {\taprefix Prof. M. Ebadzadeh} % Professor
    {\autsite{short}} % Location
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Multicore Programming} % Course
    {\taprefix Prof. M. Momtazpour} % Professor
    {\autsite{short}} % Location
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Signals and Systems} % Course
    {\textbf{Head} \taprefix Prof. M. Rasti} % Professor
    {\autsite{short}} % Location
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Data Structures and Algorithms} % Course
    {\taprefix Prof. E. Nazerfard} % Professor
    {\autsite{short}} % Location
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Linear Algebra} % Course
    {\taprefix Prof. M. H. Chehreghani} % Professor
    {\autsite{short}} % Location
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Signals and Systems} % Course
    {\taprefix Dr. A. Aghaeeyan} % Professor
    {\autsite{short}} % Location
    {2021} % Date(s)

\end{cvhonors}
