%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------  
  \cventry
    {Python, Keras, PyTorch, Genrative Models} % Skills
    {Generating Handwritten Persian Characters with Generative Models} % Project
    {} % Empty location
    {Feb. 2022 - Apr. 2023} % Date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Evaluated and analyzed  \textbf{generative models} ability to represent and reconstruct individual Persian handwritten characters. The studied models were \href{https://arxiv.org/abs/1406.2661}{\textbf{GAN}} and its variations (like \href{https://arxiv.org/abs/1511.06434}{\textbf{DCGAN}} and \href{https://arxiv.org/abs/1704.00028}{\textbf{WGAN-GP}}), \href{https://arxiv.org/abs/1312.6114}{\textbf{VAE}}, \href{https://arxiv.org/abs/1605.08803}{\textbf{Real NVP} (Normalizing Flows)}, and \href{https://arxiv.org/abs/2006.11239}{\textbf{DDPM}}.}
      	\item{Trained a Real NVP model and employed a \textit{novel technique} to \textbf{replicate personal handwriting styles} based on sample data. Final \textbf{BSc.~project} under Prof.~A.~Nickabadi.}
      \end{cvitems}
    }

  \cventry
    {Python} % Skills
    {\href{https://github.com/radinshayanfar/AUT-IR}{Information Retrieval Engine}} % Project
    {} % Empty location
    {2022} % Date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Built a text-based search engine with support for \textbf{Boolean} and \textbf{TF-IDF ranked retrieval}, using a positional inverted index in \textbf{Python}.}
      \end{cvitems}
    }

%---------------------------------------------------------  
  \cventry
    {Python, NumPy, Signals and Systems} % Skills
    {Music Identification} % Project
    {} % Empty location
    {Spring 2021} % Date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {\textbf{Designed and implemented} a music identification and discovery system using \textbf{Fast Fourier Transform (FFT)} to generate audio fingerprints from scratch. The system computes a song's \textbf{spectrogram} by windowing the time-domain signal and calculating successive FFTs.}
        \item {Constructed fingerprints by: (1) filtering out low and high-frequency noise, (2) binning the spectrogram's frequency axis, and (3) extracting peak-magnitude frequencies from each bin as time-slice representatives. Fingerprints are compared using a custom similarity metric.}
        \item {Developed and assigned this project as the final assignment for the undergraduate \textbf{Signals and Systems} course in my role as teaching assistant.}
      \end{cvitems}
    }

%---------------------------------------------------------  
  \cventry
    {Python, Keras, OpenCV} % Skills
    {Captcha Solver} % Project
    {} % Empty location
    {2019 - 2020} % Date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Built a system to solve CAPTCHA images using \textbf{OpenCV}-based image preprocessing and a \textbf{neural network} model built with \textbf{Keras}.}
        \item {Collected and annotated training data using a custom-built web-based annotation UI.}
        \item {Trained a deep learning model on the labeled dataset and achieved \textbf{96\% accuracy} on 5-character alphanumeric CAPTCHAs.}
      \end{cvitems}
    }
    
%---------------------------------------------------------  
  \cventry
    {Laravel, MySQL, Redis, REST API} % Skills
    {Habco} % Project
    {} % Empty location
    {2021} % Date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Developed a \textbf{RESTful API} using \textbf{Laravel} for Habco, a Canadian healthcare startup serving patients, doctors, nurses, and pharmacists, enabling features like prescription sharing, drug inventory, and SMS-based authentication.}
      \end{cvitems}
    }

%---------------------------------------------------------  
%  \cventry
%    {PHP, HTML, CSS, Bootstrap, Sass, JavaScript} % Skills
%    {\href{https://samcode.allamehelli3.ir/}{SamCode Website}} % Project
%    {} % Empty location
%    {2020} % Date
%    {
%      \begin{cvitems} % Description(s) bullet points
%      	\item {Design and development of SamCode programming contest website (Held by \href{http://helli3school.ir}{Allameh Helli 3 Junior High School}).}
%      	\item {The website uses \textbf{Datalife Engine (DLE) CMS} and my work involved design and development of a \textbf{new template} for the CMS. The template is created by merging a simple landing page with DLE's default template.}
%      \end{cvitems}
%    }

%---------------------------------------------------------    
%  \cventry
%    {Java, Swing} % Skills
%    {\href{https://github.com/radinshayanfar/Jpotify}{Jpotify}} % Project
%    {} % Empty location
%    {2019} % Date
%    {
%      \begin{cvitems} % Description(s) bullet points
%        \item {Development of a graphical music player, written in Java using Swing library for UI design.}
%		\item {The player has features like playlists and music sharing with friends over network.}
%      \end{cvitems}
%    }

%---------------------------------------------------------  
%  \cventry
%    {C++, OpenCV} % Skills
%    {Ping-Pong Ball Tracker} % Project
%    {} % Empty location
%    {2014} % Date
%    {
%      \begin{cvitems} % Description(s) bullet points
%        \item {Development of a ping-pong game ball tracker using C++ and OpenCV features.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
